Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-06 writeup/gz_hubble_data.tex
Explicitly mark to-do as notes in red.

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

@@

In the FERENGI data, we find that this places large limitations on the amount of information we can extract for the higher order questions. We require that at least 5 users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher $z$. This requirement placed on both images is not met by a significant number of galaxies for questions beyond question 1. Without sufficient galaxies in each surface brightness/redshift bin, we cannot accurately measure a relationship between vote fractions and redshift; for this reason we only offer debiased vote fractions for question 1. \textbf{perhaps compute number of galaxies that can be fit to zeta for each question, show a table? overkill?} In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.

\begin{itemize}
\item talk about where the \hst{} sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debias them  
\end{itemize}

@@

To include: detailed description of each column in the machine-readable tables.

@@

\section{Using the catalog}\label{sec:cookbook}
Include cookbook for selecting morphologies.

@@

\textit{Address trends seen in broad morphological classes, possible reasons for difference. Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}

>>>>

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to $w=1.0$

{\note STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

@@

In the FERENGI data, we find that this places large limitations on the amount of information we can extract for the higher order questions. We require that at least 5 users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher $z$. This requirement placed on both images is not met by a significant number of galaxies for questions beyond question 1. Without sufficient galaxies in each surface brightness/redshift bin, we cannot accurately measure a relationship between vote fractions and redshift; for this reason we only offer debiased vote fractions for question 1.

{\note Perhaps compute number of galaxies that can be fit to zeta for each question, show a table? overkill?}

In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.

{\note
\begin{itemize}
\item talk about where the \hst{} sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debias them  
\end{itemize}
}

@@

{\note To include: detailed description of each column in the machine-readable tables. }

\section{Using the catalog}\label{sec:cookbook}

Include cookbook for selecting morphologies.

@@

@@

{\note \textit{Address trends seen in broad morphological classes, possible reasons for difference. Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}}
